Improving disaggregation models of malaria incidence by ensembling non-linear models of prevalence

### 2019-10-24 tim-lucas-model-ensembles.tex
Comment out big table.

\begin{table}
\caption{Fitted regression parameters of the environmental and machine learning covariates for thee models: just environmental variables, just local machine learning models and the combination of the two.}
\centering
\tiny
\begin{tabular}{ll|rrr}
Country    & Variable &  $\beta_{enviro}$   & $\beta_l$ & $\beta_{enviro+l}$\\ \hline
Madagascar & LST mean & 0.17 &  &  -0.01\\
Madagascar & EVI & 0.32 &  & -0.04 \\
Madagascar & TSI & 0.42 &  &0.06  \\
Madagascar & access & 0.34 &  &0.00  \\
Madagascar & Elev & -0.14 &  & 0.00\\ 
Madagascar & LST sd & -0.78 &  &-0.04  \\
Madagascar & VIIRS & -0.1 &  &-0.52  \\
Madagascar & TCW & -0.22 &  & -0.06\\ 
Madagascar & RF &  & 0.29 &  0.01\\
Madagascar & GBM &  & 0.52 & 0.25 \\
Madagascar & enet &  & 0.31 &0.09  \\
Madagascar & nnet &  & 0.43 &0.14  \\
Madagascar & ppr &  & 0.49 & 0.22\vspace{0.2cm}\\ 
Colombia & LST mean &-0.12  &  & -0.22\\
Colombia & EVI &  -0.08&  & 0.17\\
Colombia & TSI &  0.54&  & -0.06\\
Colombia & access &  0.35&  &0.00 \\
Colombia & Elev &  0.47&  & 0.00\\
Colombia & LST sd & -0.11 &  & -0.10\\
Colombia & VIIRS & 0.24 &  & 0.01\\
Colombia & TCW &  0.21&  & 0.00\\
Colombia & RF &  & 0.36 & -0.18\\
Colombia & GBM &  & 0.54 & 0.26\\
Colombia & enet &  & 0.32 & -0.34\\
Colombia & nnet &  &0.33  & -0.09\\
Colombia & ppr &  & 0.54 & 0.01\vspace{0.2cm}\\
Senegal & LST mean &-0.04  &  &-0.02\\
Senegal & EVI &  0.33&  & 0.30\\
Senegal & TSI &  -0.58&  &  -0.59\\
Senegal & access & -0.03 &  &  -0.05\\
Senegal & Elev &  0.42&  &0.37\\ 
Senegal & LST sd &  0.21&  & 0.10 \\
Senegal & VIIRS &  0.13&  &  0.13\\
Senegal & TCW & 0.08 &  &-0.01\\ 
Senegal & RF &  & 0.34 &  0.20\\
Senegal & GBM &  &  0.28& 0.05\\
Senegal & enet &  &  0.27&  -0.05\\
Senegal & nnet &  & 0.29 &-0.09 \\
Senegal & ppr &  &  0.35& 0.25\vspace{0.2cm}\\
Indonesia & LST mean & -0.32 &  &-0.34\\
Indonesia & EVI &  0.49&  & 0.36\\
Indonesia & TSI &  0.58&  &0.52\\
Indonesia & access &0.33 &  & 0.06 \\
Indonesia & Elev& -0.06&  &-0.13\\ 
Indonesia & LST sd & -0.23 &  & -0.33\\
Indonesia & VIIRS &  -0.12&  & 0.03\\
Indonesia & TCW& 0.12 &  &0.10\\ 
Indonesia & RF &  & 0.32 & 0.06\\
Indonesia & GBM &  &  0.38&0.03\\
Indonesia & enet &  &  0.49&  0.56\\
Indonesia & nnet &  &  0.36&  0.18\\
Indonesia & ppr &  &  0.45& 0.32\\

\end{tabular}
\label{t:mlresults2}
\end{table}

>>>>

%\begin{table}
%\caption{Fitted regression parameters of the environmental and machine learning covariates for thee models: just environmental variables, just local machine learning models and the combination of the two.}
%\centering
%\tiny
%\begin{tabular}{ll|rrr}
%Country    & Variable &  $\beta_{enviro}$   & $\beta_l$ & $\beta_{enviro+l}$\\ \hline
%Madagascar & LST mean & 0.17 &  &  -0.01\\
%Madagascar & EVI & 0.32 &  & -0.04 \\
%Madagascar & TSI & 0.42 &  &0.06  \\
%Madagascar & access & 0.34 &  &0.00  \\
%Madagascar & Elev & -0.14 &  & 0.00\\ 
%Madagascar & LST sd & -0.78 &  &-0.04  \\
%Madagascar & VIIRS & -0.1 &  &-0.52  \\
%Madagascar & TCW & -0.22 &  & -0.06\\ 
%Madagascar & RF &  & 0.29 &  0.01\\
%Madagascar & GBM &  & 0.52 & 0.25 \\
%Madagascar & enet &  & 0.31 &0.09  \\
%Madagascar & nnet &  & 0.43 &0.14  \\
%Madagascar & ppr &  & 0.49 & 0.22\vspace{0.2cm}\\ 
%Colombia & LST mean &-0.12  &  & -0.22\\
%Colombia & EVI &  -0.08&  & 0.17\\
%Colombia & TSI &  0.54&  & -0.06\\
%Colombia & access &  0.35&  &0.00 \\
%Colombia & Elev &  0.47&  & 0.00\\
%Colombia & LST sd & -0.11 &  & -0.10\\
%Colombia & VIIRS & 0.24 &  & 0.01\\
%Colombia & TCW &  0.21&  & 0.00\\
%Colombia & RF &  & 0.36 & -0.18\\
%Colombia & GBM &  & 0.54 & 0.26\\
%Colombia & enet &  & 0.32 & -0.34\\
%Colombia & nnet &  &0.33  & -0.09\\
%Colombia & ppr &  & 0.54 & 0.01\vspace{0.2cm}\\
%Senegal & LST mean &-0.04  &  &-0.02\\
%Senegal & EVI &  0.33&  & 0.30\\
%Senegal & TSI &  -0.58&  &  -0.59\\
%Senegal & access & -0.03 &  &  -0.05\\
%Senegal & Elev &  0.42&  &0.37\\ 
%Senegal & LST sd &  0.21&  & 0.10 \\
%Senegal & VIIRS &  0.13&  &  0.13\\
%Senegal & TCW & 0.08 &  &-0.01\\ 
%Senegal & RF &  & 0.34 &  0.20\\
%Senegal & GBM &  &  0.28& 0.05\\
%Senegal & enet &  &  0.27&  -0.05\\
%Senegal & nnet &  & 0.29 &-0.09 \\
%Senegal & ppr &  &  0.35& 0.25\vspace{0.2cm}\\
%Indonesia & LST mean & -0.32 &  &-0.34\\
%Indonesia & EVI &  0.49&  & 0.36\\
%Indonesia & TSI &  0.58&  &0.52\\
%Indonesia & access &0.33 &  & 0.06 \\
%Indonesia & Elev& -0.06&  &-0.13\\ 
%Indonesia & LST sd & -0.23 &  & -0.33\\
%Indonesia & VIIRS &  -0.12&  & 0.03\\
%Indonesia & TCW& 0.12 &  &0.10\\ 
%Indonesia & RF &  & 0.32 & 0.06\\
%Indonesia & GBM &  &  0.38&0.03\\
%Indonesia & enet &  &  0.49&  0.56\\
%Indonesia & nnet &  &  0.36&  0.18\\
%Indonesia & ppr &  &  0.45& 0.32\\
%
%
%
%\end{tabular}
%\label{t:mlresults2}
%\end{table}
%
